Composition-climate paper

### 2015-05-14 Composition_Ecology.Rmd

Whe we examine the taxa seperately we can see that by far the majority of comparisons show greater differences due to climate change than due to shifts in distribution:

>>>>

When we examine the taxa seperately we can see that by far the majority of comparisons show greater differences due to climate change than due to shifts in distribution:
